---
title: "Even code"
output:
  html_document:
    df_print: paged
---

Loading required packages:

```{r}
library(plyr)
library(ggplot2)
```

Loading MCMCglmm 
```{r}
library(MCMCglmm)
library(parallel)
library(coda)
```

Import data from files

```{r}
mondf <- function(d1, d2) {
  if (!requireNamespace("lubridate", quietly = TRUE)) {
    stop("lubridate needed for this function to work. Please install it.",
         call. = FALSE)
  }
  library(lubridate)
  
  monnb <- function(d) { lt <- as.POSIXlt(as.Date(d, origin="1900-01-01")); lt$year*12 + lt$mon }
  monnb(d2) - monnb(d1)
}

exp1_data <- read.csv("../data/exp1-child/exp1-child.csv", header=TRUE, na.strings="")
exp2_data <- read.csv("../data/exp2-child/exp2-child.csv", header=TRUE, na.strings="")

clean_data <- function(experiment, halved, filler_halved, filler_acc, ignore_kanga=FALSE) {
  # get data from the right experiment, do exclusions
  if (experiment == 1) unprocessed_data = subset(exp1_data, subject != 21 & subject != 37 & subject != 14)
  if (experiment == 2) unprocessed_data = subset(exp2_data, age_group != "6" & is.na(exclude) & is.na(exclude2) & is.na(exclude3))
  
  data = unprocessed_data
  
  # halve the data, if needed
  if (halved == "first_half")   data = subset(data, item < 7)
  else if (halved == "second_half") data = subset(data, item >= 7) 
  
  #change experiment name
  data$experiment = paste("Exp", as.character(experiment))
  
  #calculate months old
  data$month <- mondf(data$DOB, data$DOT)
  
  #Age group to text
  data$age_group <- as.character(data$age_group)
  
  #add opposite/middle columns
  data$opposite <- ifelse(data$response_type=="opposite", 1, 0)
  data$middle <- ifelse(data$response_type=="middle", 1, 0)
  
  #add relationship column
  data$relationship = ifelse(data$label=="target", ifelse(is.element(data$story, c("reach", "weight")), "direct", "inverse"), "")
  data$scenario = paste(substr(data$condition, 1, 2), substr(data$condition, 4,4), sep="")
  
  #do we calculate the filler accuracy on the halved data or on all the data?
  if (filler_halved == TRUE) {
    filler_data <- subset(data, label=="filler")
  }
  else {
    filler_data <- subset(unprocessed_data, label=="filler")
  }
  
  #do we ignore the kangaroo story?
  if (ignore_kanga == TRUE) {
    filler_data <- subset(filler_data, condition != "FSP")
  }
    
  #calculate filler accuracy
  filler.accuracy <- ddply(filler_data, .(subject), summarise, filler.accuracy = mean(correct, na.rm=TRUE))
  data <- merge(data, filler.accuracy)
  
  #filter out those who scored less than filler_acc
  data$good.acc <- ifelse(data$filler.accuracy >= filler_acc, 1, 0)
  filtered_data <- subset(data, good.acc == 1)
  
  #calculate means and error bars
  al.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(correct, na.rm=TRUE))
  al.sd <- ddply(al.accuracy, .(age_group, polarity), summarise, al_sd=sd(accuracy, na.rm=TRUE), al_accuracy=mean(accuracy, na.rm=TRUE))
  
  middle.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(middle, na.rm=TRUE))
  middle.sd <- ddply(middle.accuracy, .(age_group, polarity), summarise, mid_sd=sd(accuracy, na.rm=TRUE), mid_accuracy=mean(accuracy, na.rm=TRUE))
  
  opposite.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(opposite, na.rm=TRUE))
  opposite.sd <- ddply(opposite.accuracy, .(age_group, polarity), summarise, opp_sd=sd(accuracy, na.rm=TRUE), opp_accuracy=mean(accuracy, na.rm=TRUE))
  
  #merge into data
  filtered_data <- merge(filtered_data, al.sd)
  filtered_data <- merge(filtered_data, middle.sd)
  filtered_data <- merge(filtered_data, opposite.sd)
  filtered_data <- merge(filtered_data, filler.accuracy)
  
  filtered_data$age_group <- as.factor(filtered_data$age_group)
  filtered_data$subject <- as.factor(filtered_data$subject)
  
  return(filtered_data)
  
}

clean.data.all.exp1 <- clean_data(experiment=1, halved="all", filler_halved=FALSE, filler_acc=0.75)
clean.data.first_half.exp1 <- clean_data(experiment=1, halved="first_half", filler_halved=FALSE, filler_acc=0.1)
clean.data.first_half.exp2 <- clean_data(experiment=2, halved="first_half", filler_halved=FALSE, filler_acc=0.75)
clean.data.second_half.exp2 <- clean_data(experiment=2, halved="second_half", filler_halved=FALSE, filler_acc=0.75)
clean.data.all.exp2 <- clean_data(experiment=2, halved="all", filler_halved=FALSE, filler_acc=0.75)

```

Helper functions

```{r}
targ <- function(data) { 
  
  subsetted <- subset(data, label=="target")
  
  subsetted$midresponse <- ifelse(subsetted$response_type=="middle", 1,0)
  subsetted$mostlikely <- ifelse(subsetted$polarity=="neg" & subsetted$response_type == "adult-like", 1, ifelse(subsetted$polarity=="pos" & subsetted$response_type == "opposite", 1,0))
  subsetted$leastlikely <- ifelse(subsetted$polarity=="neg" & subsetted$response_type=="opposite", 1, ifelse(subsetted$polarity=="pos" & subsetted$response_type == "adult-like", 1, 0))
  
  return(droplevels(subsetted))
}
```

** Experiment 1 **

Analysis for first experiment with MCMCglmm:

```{r}
indata_exp1 <- subset(clean.data.first_half.exp1, response_type %in% c("adult-like", "opposite", "middle"))

chisq.test(table(targ(subset(indata_exp1, age_group == 3))$response_type))
chisq.test(table(targ(subset(indata_exp1, age_group == 4))$response_type))
chisq.test(table(targ(subset(indata_exp1, age_group == 5))$response_type))
chisq.test(table(targ(subset(indata_exp1, age_group == 6))$response_type))


```
Based on section 5.2 of https://cran.r-project.org/web/packages/MCMCglmm/vignettes/CourseNotes.pdf as well as https://hlplab.wordpress.com/2009/05/07/multinomial-random-effects-models-in-r/ and http://www.natalialevshina.com/Documents/MCMCglmm_Tutorial.pdf https://github.com/tmalsburg/MCMCglmm-intro

Prior: "For reasons that will become clearer later I like to work with the residual covariance matrix 1/J * (I + J) where I and J are J − 1 dimensional identity and unit matrices, respectively."

response_type: {"adult-like", "opposite", "middle"}

-1 tells the model not to estimate a global intercept (this basically makes multinomial models easy to interpret)

+ trait tells the model to estimate an intercept by response_type

trait:(polarity + age_group)^2 all two-way interactions, as well as one-way interactions, all interacted with the different response types.

The mclapply function is essentially running 4 models in parallel. The point of this is to be able to compare the chains after the fact to see if they converge on the same values. This serves as a convergence test.

```{r}
IJ <- (1/3) * (diag(2) + matrix(1,2,2))
prior.MC <- list(R = list(V = IJ, fix = 1),
                 G=list(G1=list(V        = diag(2),
                                n        = 2),
                        G2=list(V        = diag(2),
                                n        = 2)))

exp1_ag_fixed_formula <- formula(response_type ~ -1 + trait + trait:(polarity + age_group)^2)
exp1_m_fixed_formula <- formula(response_type ~ -1 + trait + trait:(polarity + month)^2)
exp1_random_formula <- formula(~ us(trait):subject + us(trait):condition)

set.seed(1)

model_MC_exp1 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = exp1_ag_fixed_formula,
                     random = exp1_random_formula,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata_exp1),
                     prior=prior.MC,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)


model_MC_exp1_month <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = exp1_m_fixed_formula,
                     random = exp1_random_formula,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata_exp1),
                     prior=prior.MC,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
  }, mc.cores=4)
                     

                     
```
Here, we're running something known as the Gelman-Rubin diagnostic, which basically asks how similar all four different Markov chains are. It gives you a value, the PSRF, which asks, if you were to keep running this chain, how many times bigger could this value get? The closer that the PSRF is to 1, the more confident we can be that the model has converged. As we can see, our chains are basically identical, which gives us a good deal of confidence that we can trust the results of this model.

```{r}
model_MC_exp1_diag <- lapply(model_MC_exp1, function(m) m$Sol)
model_MC_exp1_diag <- do.call(mcmc.list, model_MC_exp1_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp1_diag, auto.layout=F)
gelman.diag(model_MC_exp1_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp1_diag, ask=F, auto.layout=F)

```
Now we do the same for the month model.
```{r}
model_MC_exp1_month_diag <- lapply(model_MC_exp1_month, function(m) m$Sol)
model_MC_exp1_month_diag <- do.call(mcmc.list, model_MC_exp1_month_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp1_month_diag, auto.layout=F)
gelman.diag(model_MC_exp1_month_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp1_month_diag, ask=F, auto.layout=F)



```
```{r}
plot.estimates <- function(x) {
  if (class(x) != "summary.mcmc")
    x <- summary(x)
  n <- dim(x$statistics)[1]
  par(mar=c(2, 25, 4, 1))
  plot(x$statistics[,1], n:1,
       yaxt="n", ylab="",
       xlim=range(x$quantiles)*1.2,
       pch=19,
       main="Posterior means and 95% credible intervals")
  grid()
  axis(2, at=n:1, rownames(x$statistics), las=2)
  arrows(x$quantiles[,1], n:1, x$quantiles[,5], n:1, code=0)
  abline(v=0, lty=2)
}

plot.estimates(model_MC_exp1_diag)
plot.estimates(model_MC_exp1_month_diag)

summary(model_MC_exp1_diag)
summary(model_MC_exp1_month_diag)
```



Analysis for second experiment
```{r}
indata_exp2 <- subset(clean.data.all.exp2, response_type %in% c("adult-like", "opposite", "middle"))

chisq.test(table(targ(subset(indata_exp2, age_group == 3))$response_type))
chisq.test(table(targ(subset(indata_exp2, age_group == 4))$response_type))
chisq.test(table(targ(subset(indata_exp2, age_group == 5))$response_type))

``` 

```{r}
IJ <- (1/3) * (diag(2) + matrix(1,2, 2))
prior.MC2 <- list(R = list(V = IJ, fix = 1),
                 G=list(G1=list(V        = diag(2),
                                n        = 2),
                        G2=list(V        = diag(2),
                                n        = 2),
                        G3=list(V        = diag(2),
                                n        = 2)))


model_MC_exp2 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = response_type ~ -1 + trait + trait:(polarity + order + age_group)^3,
                     random = ~ us(trait):subject + us(trait):condition + us(order):condition,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata),
                     prior=prior.MC2,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)


model_MC_exp2_month <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = response_type ~ -1 + trait + trait:(polarity + order + month)^3,
                     random = ~ us(trait):subject + us(trait):condition + us(order):condition,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata),
                     prior=prior.MC2,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
                     
```
Running convergence diagnostics for this model:
```{r}
model_MC_exp2_diag <- lapply(model_MC_exp2, function(m) m$Sol)
model_MC_exp2_diag <- do.call(mcmc.list, model_MC_exp2_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp2_diag, auto.layout=F)
gelman.diag(model_MC_exp2_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp2_diag, ask=F, auto.layout=F)



```
Now we do the same for the month model.
```{r}
model_MC_exp2_month_diag <- lapply(model_MC_exp2_month, function(m) m$Sol)
model_MC_exp2_month_diag <- do.call(mcmc.list, model_MC_exp2_month_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp2_month_diag, auto.layout=F)
gelman.diag(model_MC_exp2_month_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp2_month_diag, ask=F, auto.layout=F)



```


```{r}

plot.estimates(model_MC_exp2_diag)
plot.estimates(model_MC_exp2_month_diag)

summary(model_MC_exp2_diag)
summary(model_MC_exp2_month_diag)
```
```{r}
model_MC_exp2_att2 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = response_type ~ -1 + trait + trait:(polarity + age_group)^2 + trait:order,
                     random = ~ us(trait):subject + us(trait):condition + us(order):condition,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata),
                     prior=prior.MC2,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)


model_MC_exp2_month_att2 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = response_type ~ -1 + trait + trait:(polarity + month)^2 + trait:order,
                     random = ~ us(trait):subject + us(trait):condition + us(order):condition,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata),
                     prior=prior.MC2,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
```



```{r}
model_MC_exp2_diag_att2 <- lapply(model_MC_exp2_att2, function(m) m$Sol)
model_MC_exp2_diag_att2 <- do.call(mcmc.list, model_MC_exp2_diag_att2)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp2_diag_att2, auto.layout=F)
gelman.diag(model_MC_exp2_diag_att2)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp2_diag_att2, ask=F, auto.layout=F)


```



```{r}
plot.estimates(model_MC_exp2_diag_att2)

summary(model_MC_exp2_diag_att2)
```
```{r}
model_MC_exp2_att3 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = response_type ~ -1 + trait + trait:(polarity + order + age_group)^2,
                     random = ~ us(trait):subject + us(trait):condition + us(order):condition,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata),
                     prior=prior.MC2,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)

model_MC_exp2_month_att3 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = response_type ~ -1 + trait + trait:(polarity + order + month)^2,
                     random = ~ us(trait):subject + us(trait):condition + us(order):condition,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata),
                     prior=prior.MC2,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
```


```{r}
model_MC_exp2_diag_att3 <- lapply(model_MC_exp2_att3, function(m) m$Sol)
model_MC_exp2_diag_att3 <- do.call(mcmc.list, model_MC_exp2_diag_att3)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp2_diag_att3, auto.layout=F)
gelman.diag(model_MC_exp2_diag_att3)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp2_diag_att3, ask=F, auto.layout=F)
```

```{r}
plot.estimates(model_MC_exp2_diag_att3)

summary(model_MC_exp2_diag_att3)
```

```{r}
model_MC_exp2_month_diag_att3 <- lapply(model_MC_exp2_month_att3, function(m) m$Sol)
model_MC_exp2_month_diag_att3 <- do.call(mcmc.list, model_MC_exp2_month_diag_att3)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp2_month_diag_att3, auto.layout=F)
gelman.diag(model_MC_exp2_month_diag_att3)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp2_month_diag_att3, ask=F, auto.layout=F)


```

```{r}
plot.estimates(model_MC_exp2_month_diag_att3)

summary(model_MC_exp2_month_diag_att3)
```

Now, rescaling intercepts/coefficients:


```{r}
c2 <- (16 * sqrt(3)/(15 * pi))^2
Delta <- cbind(c(-1, 1, 0), c(-1, 0, 1))
D <- ginv(Delta %*% t(Delta)) %*% Delta
bind_mcmc = function(x) {
  do.call(rbind.data.frame, x)
}

model_MC_exp1_combined <- bind_mcmc(model_MC_exp1_diag)
model_MC_exp2_combined <- bind_mcmc(model_MC_exp2_diag_att3)

rescale = function(model, int) {
  rescaled <- t(apply(model[, int], 1, function(x) {
  D %*% (x/sqrt(1 + c2 * diag(IJ)))
}))
  colnames(rescaled) <- c("adult", "middle", "opposite")
  return(rescaled)
}

exp1_int <- rescale(model_MC_exp1_combined, 1:2)

exp1_pos <- rescale(model_MC_exp1_combined, 3:4)

exp1_age_4 <- rescale(model_MC_exp1_combined, 5:6)

exp1_age_5 <- rescale(model_MC_exp1_combined, 7:8)

exp1_age_6 <- rescale(model_MC_exp1_combined, 9:10)

exp1_pos_age_4 <- rescale(model_MC_exp1_combined, 11:12)

exp1_pos_age_5 <- rescale(model_MC_exp1_combined, 5:6)

exp1_pos_age_6 <- rescale(model_MC_exp1_combined, 5:6)

exp2_int <- rescale(model_MC_exp2_combined, 1:2)

exp2_pos <- rescale(model_MC_exp2_combined, 3:4)

exp2_orders <- rescale(model_MC_exp2_combined, 5:6)

exp2_age_4 <- rescale(model_MC_exp2_combined, 7:8)

exp2_age_5 <- rescale(model_MC_exp2_combined, 9:10)

exp2_pos_orders <- rescale(model_MC_exp2_combined, 11:12)

exp2_pos_age_4 <- rescale(model_MC_exp2_combined, 13:14)

exp2_pos_age_5 <- rescale(model_MC_exp2_combined, 15:16)

exp2_orders_age_4 <- rescale(model_MC_exp2_combined, 17:18)

exp2_orders_age_5 <- rescale(model_MC_exp2_combined, 19:20)

formula_exp1 = function(polarity, age) {
  exp1_int + 
    (polarity == "pos")*exp1_pos + 
    (age == 4)*exp1_age_4 + 
    (age == 5)*exp1_age_5 + 
    (age == 6)*exp1_age_6 +
    (age == 4)*(polarity == "pos")*exp1_pos_age_4 + 
    (age == 5)*(polarity == "pos")*exp1_pos_age_5 + 
    (age == 6)*(polarity == "pos")*exp1_pos_age_6
}

formula_exp2 = function(polarity, order, age) {
  exp2_int + 
    (polarity == "pos")*exp2_pos + 
    (order == "s")*exp2_orders +
    (age == 4)*exp2_age_4 + 
    (age == 5)*exp2_age_5 + 
    (age == 4)*(polarity == "pos")*exp2_pos_age_4 + 
    (age == 5)*(polarity == "pos")*exp2_pos_age_5 + 
    (age == 4)*(order == "s")*exp2_orders_age_4 + 
    (age == 5)*(order == "s")*exp2_orders_age_5 + 
    (order == "s")*(polarity == "pos")*exp2_pos_orders
  }

single_point = function(vars, prob=.95) {
  mcmc <- mcmc(exp(vars)/rowSums(exp(vars)))
  print(summary(mcmc))
  HPDinterval(mcmc, prob)
}

var_difference = function(vars1, vars2, prob=.95){
 mcmc <- mcmc((exp(vars1)/rowSums(exp(vars1))) - (exp(vars2)/rowSums(exp(vars2))))
 print(summary(mcmc))
 HPDinterval(mcmc, prob)
}

var_sums = function(..., prob=.95) {
  vars <- list(...)
  num <- Reduce("+", lapply(vars, function(x) { exp(x)  } ))
  denom <- Reduce("+", lapply(vars, function(x) { rowSums(exp(x))  } ))
  mcmc <- mcmc(num / denom)
  print(summary(mcmc))
  HPDinterval(mcmc, prob)
}

var_diff_sums = function(vars1, vars2, vars3, vars4, prob=.95) {
  mcmc <- mcmc((exp(vars1) + exp(vars2))/(rowSums(exp(vars1)) + rowSums(exp(vars2)))
               - (exp(vars3) + exp(vars4))/(rowSums(exp(vars3)) + rowSums(exp(vars4))))
  print(summary(mcmc))
  HPDinterval(mcmc, prob)
}

```
Analysis of justifications
```{r}
IJ <- (1/3) * (diag(2) + matrix(1,2,2))
prior.MC <- list(R = list(V = IJ, fix = 1),
                 G=list(G1=list(V        = diag(2),
                                n        = 2),
                        G2=list(V        = diag(2),
                                n        = 2)))

exp1_just_fixed_formula <- formula(just_type ~ -1 + trait + trait:(response_type + polarity + age_group))
exp1_just_random_formula <- formula(~ us(trait):subject + us(trait):condition)

indata_exp1_just <- droplevels(subset(clean.data.first_half.exp1, response_type %in% c("adult-like", "opposite", "middle")))
indata_exp1_just$just_type[is.na(indata_exp1_just$just_type)] <- "none"

model_MC_exp1_just <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = exp1_just_fixed_formula,
                     random = exp1_just_random_formula,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata_exp1_just),
                     prior=prior.MC,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
```

```{r}

model_MC_exp1_diag_just <- lapply(model_MC_exp1_just, function(m) m$Sol)
model_MC_exp1_diag_just <- do.call(mcmc.list, model_MC_exp1_diag_just)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp1_diag_just, auto.layout=F)
gelman.diag(model_MC_exp1_diag_just)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp1_diag_just, ask=F, auto.layout=F)
```

```{r}
plot.estimates(model_MC_exp1_diag_just)

summary(model_MC_exp1_diag_just)
```

```{r}
c2 <- (16 * sqrt(3)/(15 * pi))^2
Delta <- cbind(c(-1, 1, 0), c(-1, 0, 1))
D <- ginv(Delta %*% t(Delta)) %*% Delta

model_MC_exp1_just_combined <- bind_mcmc(model_MC_exp1_diag_just)

rescale_just = function(model, int) {
  rescaled <- t(apply(model[, int], 1, function(x) {
  D %*% (x/sqrt(1 + c2 * diag(IJ)))
}))
  colnames(rescaled) <- c("none", "random", "scale")
  return(rescaled)
}

exp1_just_int <- rescale_just(model_MC_exp1_just_combined, 1:2)
exp1_just_middle <- rescale_just(model_MC_exp1_just_combined, 3:4)
exp1_just_opposite <- rescale_just(model_MC_exp1_just_combined, 5:6)
exp1_just_pos <- rescale_just(model_MC_exp1_just_combined, 7:8)
exp1_just_4 <- rescale_just(model_MC_exp1_just_combined, 9:10)
exp1_just_5 <- rescale_just(model_MC_exp1_just_combined, 11:12)
exp1_just_6 <- rescale_just(model_MC_exp1_just_combined, 13:14)

formula_exp1_just = function(polarity, response, age) {
  exp1_just_int + 
    (polarity == "pos")*exp1_just_pos + 
    (response == "middle")*exp1_just_middle +
    (response == "opposite")*exp1_just_opposite +
    (age == 4)*exp1_just_4 + 
    (age == 5)*exp1_just_5 + 
    (age == 6)*exp1_just_6
}


gen_sums = function(...) {
  vars <- list(...)
  num <- Reduce("+", lapply(vars, function(x) { exp(x)  } ))
  denom <- Reduce("+", lapply(vars, function(x) { rowSums(exp(x))  } ))
  return(num/denom)
}

al <- gen_sums(formula_exp1_just(polarity="neg", response="adult", age=3), formula_exp1_just(polarity="pos", response="adult", age=3), formula_exp1_just(polarity="neg", response="adult", age=4), formula_exp1_just(polarity="pos", response="adult", age=4), formula_exp1_just(polarity="neg", response="adult", age=5), formula_exp1_just(polarity="pos", response="adult", age=5), formula_exp1_just(polarity="neg", response="adult", age=6), formula_exp1_just(polarity="pos", response="adult",  age=6))

opp <- gen_sums(formula_exp1_just(polarity="pos", response="opposite", age=3), formula_exp1_just(polarity="neg", response="opposite", age=3), formula_exp1_just(polarity="neg", response="opposite", age=4), formula_exp1_just(polarity="pos", response="opposite", age=4), formula_exp1_just(polarity="neg", response="opposite", age=5), formula_exp1_just(polarity="pos", response="opposite", age=5), formula_exp1_just(polarity="neg", response="opposite", age=6), formula_exp1_just(polarity="pos", response="opposite",  age=6))

mid <- gen_sums(formula_exp1_just(polarity="neg", response="middle", age=3), formula_exp1_just(polarity="pos", response="middle", age=3), formula_exp1_just(polarity="neg", response="middle", age=4), formula_exp1_just(polarity="pos", response="middle", age=4), formula_exp1_just(polarity="neg", response="middle", age=5), formula_exp1_just(polarity="pos", response="middle", age=5), formula_exp1_just(polarity="neg", response="middle", age=6), formula_exp1_just(polarity="pos", response="middle",  age=6))


alopp <- mcmc(al - opp)
almid <- mcmc(al - mid)
oppmid <- mcmc(opp - mid)

``` 
Justifications Exp2
```{r}

exp2_justifications <- read.csv("../data/exp2-child/exp2-child-justifications.csv", header=TRUE, na.strings="")

exp2_justifications <- merge(clean.data.all.exp2[,!(names(clean.data.all.exp2) == "just.type")], exp2_justifications)


IJ <- (1/3) * (diag(2) + matrix(1,2,2))
prior.MC <- list(R = list(V = IJ, fix = 1),
                 G=list(G1=list(V        = diag(2),
                                n        = 2),
                        G2=list(V        = diag(2),
                                n        = 2)))

exp2_just_fixed_formula <- formula(just.type ~ -1 + trait + trait:(response_type + polarity + order + age_group))
exp2_just_random_formula <- formula(~ us(trait):subject + us(trait):story)

indata_exp2_just <- droplevels(subset(exp2_justifications, response_type %in% c("adult-like", "opposite", "middle")))
levels(indata_exp2_just$just.type) <- c(levels(indata_exp2_just$just.type), "none")
indata_exp2_just$just.type[is.na(indata_exp2_just$just.type)] <- "none"

model_MC_exp2_just <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = exp2_just_fixed_formula,
                     random = exp2_just_random_formula,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     data = targ(indata_exp2_just),
                     prior=prior.MC,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
```


```{r}
model_MC_exp2_diag_just <- lapply(model_MC_exp2_just, function(m) m$Sol)
model_MC_exp2_diag_just <- do.call(mcmc.list, model_MC_exp2_diag_just)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_exp2_diag_just, auto.layout=F)
gelman.diag(model_MC_exp2_diag_just)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_exp2_diag_just, ask=F, auto.layout=F)

```

```{r}
c2 <- (16 * sqrt(3)/(15 * pi))^2
Delta <- cbind(c(-1, 1, 0), c(-1, 0, 1))
D <- ginv(Delta %*% t(Delta)) %*% Delta

model_MC_exp2_just_combined <- bind_mcmc(model_MC_exp2_diag_just)

rescale_just_exp2 = function(model, int) {
  rescaled <- t(apply(model[, int], 1, function(x) {
  D %*% (x/sqrt(1 + c2 * diag(IJ)))
}))
  colnames(rescaled) <- c("random", "scalar", "none")
  return(rescaled)
}

exp2_just_int <- rescale_just_exp2(model_MC_exp2_just_combined, 1:2)
exp2_just_middle <- rescale_just_exp2(model_MC_exp2_just_combined, 3:4)
exp2_just_opposite <- rescale_just_exp2(model_MC_exp2_just_combined, 5:6)
exp2_just_pos <- rescale_just_exp2(model_MC_exp2_just_combined, 7:8)
exp2_just_order <- rescale_just_exp2(model_MC_exp2_just_combined, 9:10)
exp2_just_4 <- rescale_just_exp2(model_MC_exp2_just_combined, 11:12)
exp2_just_5 <- rescale_just_exp2(model_MC_exp2_just_combined, 13:14)

formula_exp2_just = function(polarity, response, order="f", age) {
  exp2_just_int + 
    (polarity == "pos")*exp2_just_pos + 
    (response == "middle")*exp2_just_middle +
    (response == "opposite")*exp2_just_opposite +
    (order == "s")*exp2_just_order +
    (age == 4)*exp2_just_4 + 
    (age == 5)*exp2_just_5 
  }


gen_sums = function(...) {
  vars <- list(...)
  num <- Reduce("+", lapply(vars, function(x) { exp(x)  } ))
  denom <- Reduce("+", lapply(vars, function(x) { rowSums(exp(x))  } ))
  return(num/denom)
}

al_exp2 <- gen_sums(formula_exp2_just(polarity="neg", response="adult", age=3), formula_exp2_just(polarity="pos", response="adult", age=3), formula_exp2_just(polarity="neg", response="adult", age=4), formula_exp2_just(polarity="pos", response="adult", age=4), formula_exp2_just(polarity="neg", response="adult", age=5), formula_exp2_just(polarity="pos", response="adult", age=5), formula_exp2_just(polarity="neg", response="adult", order="s", age=3), formula_exp2_just(polarity="pos", response="adult", order="s", age=3), formula_exp2_just(polarity="neg", response="adult", order="s", age=4), formula_exp2_just(polarity="pos", response="adult", order="s", age=4), formula_exp2_just(polarity="neg", response="adult", order="s", age=5), formula_exp2_just(polarity="pos", response="adult", order="s", age=5))

opp_exp2 <- gen_sums(formula_exp2_just(polarity="pos", response="opposite", age=3), formula_exp2_just(polarity="neg", response="opposite", age=3), formula_exp2_just(polarity="neg", response="opposite", age=4), formula_exp2_just(polarity="pos", response="opposite", age=4), formula_exp2_just(polarity="neg", response="opposite", age=5), formula_exp2_just(polarity="pos", response="opposite", age=5), formula_exp2_just(polarity="pos", response="opposite", order="s", age=3), formula_exp2_just(polarity="neg", response="opposite", order="s", age=3), formula_exp2_just(polarity="neg", response="opposite", order="s", age=4), formula_exp2_just(polarity="pos", response="opposite", order="s", age=4), formula_exp2_just(polarity="neg", response="opposite", order="s", age=5), formula_exp2_just(polarity="pos", response="opposite", order="s", age=5))

mid_exp2 <- gen_sums(formula_exp2_just(polarity="neg", response="middle", age=3), formula_exp2_just(polarity="pos", response="middle", age=3), formula_exp2_just(polarity="neg", response="middle", age=4), formula_exp2_just(polarity="pos", response="middle", age=4), formula_exp2_just(polarity="neg", response="middle", age=5), formula_exp2_just(polarity="pos", response="middle", age=5), formula_exp2_just(polarity="neg", response="middle", order="s", age=3), formula_exp2_just(polarity="pos", response="middle", order="s", age=3), formula_exp2_just(polarity="neg", response="middle", order="s", age=4), formula_exp2_just(polarity="pos", response="middle", order="s", age=4), formula_exp2_just(polarity="neg", response="middle", order="s", age=5), formula_exp2_just(polarity="pos", response="middle", order="s", age=5))


alopp_exp2 <- mcmc(al_exp2 - opp_exp2)
almid_exp2 <- mcmc(al_exp2 - mid_exp2)
oppmid_exp2 <- mcmc(opp_exp2 - mid_exp2)
```



Analysis of adult data
```{r}
adult.data <- read.csv("../data/exp1-adult/exp1-adult.csv", header=TRUE, na.strings="NULL")



# Participant exclusion criterion running function
# Discuss principled participant exclusion criteria and age range before running this
clean_adult_data <- function(data) {
  
  unprocessed_data <- subset(data, label != "practice")

  #get just target data, filter out timeouts
  filtered_data <- subset(unprocessed_data, (label=="pos" | label=="neg") & !is.na(correct))
  
  #filtered_data$age_group <- as.character(filtered_data$age_group)
  
  #add opposite/middle columns
  #filtered_data$opposite <- ifelse(filtered_data$response_type=="opposite", 1, 0)
  #filtered_data$middle <- ifelse(filtered_data$response_type=="middle", 1, 0)
  
  
  
  # accuracy check and exclusion of low-accuracy participants
  # Accuracy criterion for inclusion in most experiments is 75% total filler accuracy (as there is only one filler condition)
  # Accuracy criterion for inclusion in conjunction only is either 100% conjunction filler accuracy, or 50% conjunction filler accuracy and 75% total filler accuracy

  target.accuracy <- ddply(filtered_data, .(WorkerId, label), summarise, target.accuracy=mean(correct, na.rm=TRUE))
  filler.accuracy <- ddply(subset(unprocessed_data, label=="fill"), .(WorkerId), summarise, filler.accuracy = mean(correct, na.rm=TRUE))
  
  target.rt <- ddply(subset(filtered_data, responseTime < 9999), .(WorkerId, label), summarise, target.rt=mean(responseTime))
  
  
  #al.accuracy_new <- ddply(subset(filtered_data, label=="target"), .(age_group, polarity), summarise, al_sd=sd(correct, na.rm=TRUE), al_accuracy=mean(correct, na.rm=TRUE), numobvs=length(correct))
  #middle.accuracy_new <- ddply(subset(filtered_data, label=="target"), .(age_group, polarity), summarise, mid_sd=sd(middle, na.rm=TRUE), mid_accuracy=mean(middle, na.rm=TRUE))
  #opposite.accuracy_new <- ddply(subset(filtered_data, label=="target"), .(age_group, polarity), summarise, opp_sd=sd(opposite, na.rm=TRUE), opp_accuracy=mean(opposite, na.rm=TRUE))
  
  
  #al.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(correct, na.rm=TRUE), numobvs=length())
  #al.sd <- ddply(al.accuracy, .(age_group, polarity), summarise, al_se=sd(accuracy, na.rm=TRUE)/sqrt(al_sd=sd(accuracy, na.rm=TRUE), al_accuracy=mean(accuracy, na.rm=TRUE))


  #middle.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(middle, na.rm=TRUE))
  #middle.sd <- ddply(middle.accuracy, .(age_group, polarity), summarise, mid_sd=sd(accuracy, na.rm=TRUE), mid_accuracy=mean(accuracy, na.rm=TRUE))
  
  #opposite.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(opposite, na.rm=TRUE))
  #opposite.sd <- ddply(opposite.accuracy, .(age_group, polarity), summarise, opp_sd=sd(accuracy, na.rm=TRUE), opp_accuracy=mean(accuracy, na.rm=TRUE))
  
    
  #unprocessed_data <- merge(unprocessed_data, overall.accuracy)
  unprocessed_data <- merge(unprocessed_data, filler.accuracy)
  unprocessed_data <- merge(unprocessed_data, target.accuracy)
  unprocessed_data <- merge(unprocessed_data, target.rt)
  
  na.count <- ddply(filtered_data, .(WorkerId), summarise, na.count=sum(is.na(answer)))
  one.count <- ddply(filtered_data, .(WorkerId), summarise, one.count=sum(answer=="1", na.rm=TRUE))
  two.count <- ddply(filtered_data, .(WorkerId), summarise, two.count=sum(answer=="2", na.rm=TRUE))
  three.count <- ddply(filtered_data, .(WorkerId), summarise, three.count=sum(answer=="3", na.rm=TRUE))

  unprocessed_data <- merge(unprocessed_data, one.count)
  unprocessed_data <- merge(unprocessed_data, two.count)
  unprocessed_data <- merge(unprocessed_data, three.count)
  unprocessed_data <- merge(unprocessed_data, na.count)
  
  # response type column
  unprocessed_data$responseType <- ifelse(unprocessed_data$answer==2, "mid", ifelse(unprocessed_data$correct==1, "adultlike", "opposite"))
  
  # other measures
  # log
  unprocessed_data$logRT = log(unprocessed_data$responseTime)
  
  # z score
  p.means <- aggregate(unprocessed_data$responseTime, list(WorkerId = unprocessed_data$WorkerId), mean)
  colnames(p.means)[2] = "mean"
  p.sds <- aggregate(unprocessed_data$responseTime, list(WorkerId = unprocessed_data$WorkerId), sd)
  colnames(p.sds)[2] = "sd"
  p.data <- merge(p.means, p.sds, by="WorkerId")
  unprocessed_data <- merge(unprocessed_data, p.data, by="WorkerId")
  unprocessed_data$zScore = (unprocessed_data$responseTime - unprocessed_data$mean)/unprocessed_data$sd
  unprocessed_data$mean <- NULL
  unprocessed_data$sd <- NULL

  #percent.yes <- ddply(unprocessed_data, .(subject), summarise, percent.yes=mean(answer))
  
  #unprocessed_data <- merge(unprocessed_data, percent.yes)
  
  # Exclude bad participants
  unprocessed_data$good.acc <- ifelse(unprocessed_data$filler.accuracy >= 0.65, 1, 0)
  unprocessed_data$same.answer <- ifelse(unprocessed_data$one.count >= 7 |
                              unprocessed_data$two.count >= 7 |
                              unprocessed_data$three.count >= 7 |
                              unprocessed_data$na.count >= 4, 1, 0)
  
  
  # exclude bad participants
  processed_data <- subset(unprocessed_data, good.acc == 1 & same.answer == 0)
  
  # insert a column for accuracy for each participant for each condition's accuracy
  #condition.accuracy <- ddply(processed_data, .(subject, condition), summarise, condition.accuracy=mean(correct))
  #processed_data <- merge(processed_data, condition.accuracy)
  
  
  return(processed_data)
  
  
  
}

clean.adult.data.exp1 <- clean_adult_data(adult.data)
```
Running RT analysis and response_type analysis on adult data.

```{r}
no_NA_exp1 <- droplevels(subset(clean.adult.data.exp1, !is.na(clean.adult.data.exp1$responseType)))

no_NA_exp1$responseType <- as.factor(no_NA_exp1$responseType)

model_MC_adult_exp1 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = logRT ~ (label + responseType)^2,
                     random = ~ WorkerId + request,
                     family = "gaussian",
                     data = no_NA_exp1,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
```

Running diagnostics on chains

```{r}
model_MC_adult_exp1_diag <- lapply(model_MC_adult_exp1, function(m) m$Sol)
model_MC_adult_exp1_diag <- do.call(mcmc.list, model_MC_adult_exp1_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_adult_exp1_diag, auto.layout=F)
gelman.diag(model_MC_adult_exp1_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_adult_exp1_diag, ask=F, auto.layout=F)
```

```{r}
model_MC_adult_exp1_combined <- bind_mcmc(model_MC_adult_exp1_diag)

adult_exp1_intercept <- model_MC_adult_exp1_combined[, 1]
adult_exp1_pos <- model_MC_adult_exp1_combined[, 2]
adult_exp1_mid <- model_MC_adult_exp1_combined[, 3]
adult_exp1_opp <- model_MC_adult_exp1_combined[, 4]
adult_exp1_posmid <- model_MC_adult_exp1_combined[, 5]
adult_exp1_posopp <- model_MC_adult_exp1_combined[, 6]

estimate_exp1 = function(polarity="neg", response_type="adult"){
  return(adult_exp1_intercept + 
         (polarity == "pos")*adult_exp1_pos +
         (response_type == "mid")*adult_exp1_mid +
         (response_type == "opp")*adult_exp1_opp +
         (polarity == "pos")*(response_type == "mid")*adult_exp1_posmid +
         (polarity == "pos")*(response_type == "opp")*adult_exp1_posopp)
}                    
```
Modeling response_type

```{r}
IJ <- (1/3) * (diag(2) + matrix(1,2, 2))
prior.MC_adult <- list(R = list(V = IJ, fix = 1),
                 G=list(G1=list(V        = diag(2),
                                n        = 2),
                        G2=list(V        = diag(2),
                                n        = 2)))


model_MC_adult_response_exp1 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = responseType ~ -1 + trait + trait:label,
                     random = ~ us(trait):WorkerId + us(trait):request,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     prior=prior.MC_adult,
                     data = no_NA_exp1,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
```

Running diagnostics on chains

```{r}
model_MC_adult_response_exp1_diag <- lapply(model_MC_adult_response_exp1, function(m) m$Sol)
model_MC_adult_response_exp1_diag <- do.call(mcmc.list, model_MC_adult_response_exp1_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_adult_response_exp1_diag, auto.layout=F)
gelman.diag(model_MC_adult_response_exp1_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_adult_response_exp1_diag, ask=F, auto.layout=F)
```

```{r}
model_MC_adult_response_exp1_combined <- bind_mcmc(model_MC_adult_response_exp1_diag)

adult_exp1_response_int <- rescale(model_MC_adult_response_exp1_combined, 1:2)

adult_exp1_response_pos <- rescale(model_MC_adult_response_exp1_combined, 3:4)
```


```{r}
clean_adult_data_exp2 <- function() {
  
  manual_excludes <- c("A3HZFB2JLF3JMY",  "A3W3VLPA3B5LJ7")
  
  `%ni%` <- Negate(`%in%`)
  
  # read in data
  # Put in the path to the folder where your data lives
  
  #read in data
  p1 <- rbind(read.csv("../data/exp2-adult/p1_batch1_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/p1_batch2_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/p1_batch3_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/p1_batch4_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/p1_batch5_results.csv", header=TRUE, na.strings="NULL"), read.csv("../data/exp2-adult/p1_batch6_results.csv", header=TRUE, na.strings="NULL"))
  p1$order <- "posfirst_1"
  
  p2 <- rbind(read.csv("../data/exp2-adult/p2_batch1_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/p2_batch2_results.csv", header=TRUE, na.strings="NULL"))
  p2$order <- "posfirst_2"
  
  n1 <- rbind(read.csv("../data/exp2-adult/n1_batch1_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/n1_batch2_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/n1_batch3_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/n1_batch4_results.csv", header=TRUE, na.strings="NULL"))
  n1$order <- "negfirst_1"
  
  n2 <- rbind(read.csv("../data/exp2-adult/n2_batch1_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/n2_batch2_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/n2_batch3_results.csv", header=TRUE, na.strings="NULL"),read.csv("../data/exp2-adult/n2_batch4_results.csv", header=TRUE, na.strings="NULL"), read.csv("../data/exp2-adult/n2_batch5_results.csv", header=TRUE, na.strings="NULL"))
  n2$order <- "negfirst_2"
  
  
  # bind these together at the beginning so that subject numbers don't overlap
  rawresults <- rbind(p1, p2, n1, n2)
  #rawresults <- rbind(p1,n1)
  results <- rawresults[grep("[\\#]", rawresults$X., invert=T),] # filter out rows that start with # symbol
  
  colnames(results) <- c("timeReceived",	"md5Hash",	"ControllerName", "ItemNumber",	"ElementNumber",	"type",	"group",	"question", "response", "correct", "responseTime", "order")
  
  
  # Assign subject numbers
  subj.dataframe <- data.frame(unique(results[, 1:2])) # creates a dataframe out of the unique identifying info md5Hash and timeReceived (md5Hash is created using the IP address)
  colnames(subj.dataframe) <- c("timeReceived",	"md5Hash")
  subj.dataframe$Subject <- 1:nrow(subj.dataframe) # assigns subject numbers
  
  # Add WorkerId info (not actually produced by PennController but end up in the same columns)
  z= subset(results, results$question=="WorkerId")[9] # take WorkerIds from the results sheet
  subj.dataframe$WorkerId <- apply(z, 2, as.character) # add WorkerIds as strings
  
  colnames(subj.dataframe) <- c("timeReceived",	"md5Hash", "Subject", "WorkerId")
  results <- merge(results, subj.dataframe, all.x=T) # puts the info back into the results for when we need it
  
  rm(z, subj.dataframe)
  
  
  # add conditions
  # Pretty sure I am doing this inside-out
  condition.vec.p1 <- c("practice", "TFP", "TRP", "FMN", "TWP", "TCP", "FSN", "FMP", "TFN", "TRN", "FSP", "TWN", "TCN")
  condition.vec.p2 <- c("practice", "TCP", "TWP", "FMN", "TRP", "TFP", "FSN", "FMP", "TCN", "TWN", "FSP", "TRN", "TFN")
  condition.vec.n1 <- c("practice", "TFN", "TRN", "FMN", "TWN", "TCN", "FSN", "FMP", "TFP", "TRP", "FSP", "TWP", "TCP")
  condition.vec.n2 <- c("practice", "TCN", "TWN", "FMN", "TRN", "TFN", "FSN", "FMP", "TCP", "TWP", "FSP", "TRP", "TFP")
  conditions.dataframe <- data.frame("pos1"=condition.vec.p1, "pos2"=condition.vec.p2, "neg1"=condition.vec.n1, "neg2"=condition.vec.n2)
  conditions.dataframe$group <- 1:13
  rm(condition.vec.n1, condition.vec.n2, condition.vec.p1, condition.vec.p2)
  
  p1.cond <- conditions.dataframe[,c(1,5)]
  colnames(p1.cond) <- c("condition", "group")
  p2.cond <- conditions.dataframe[,c(2,5)]
  colnames(p2.cond) <- c("condition", "group")
  n1.cond <- conditions.dataframe[,c(3,5)]
  colnames(n1.cond) <- c("condition", "group")
  n2.cond <- conditions.dataframe[,c(4,5)]
  colnames(n2.cond) <- c("condition", "group")
  
  # split them up to add conditions, then re-bind
  # Yadav I apologize for this code
  p1.results <- subset(results, order=="posfirst_1")
  p1.results <- merge(p1.results, p1.cond, all.x=T)
  p2.results <- subset(results, order=="posfirst_2")
  p2.results <- merge(p2.results, p2.cond, all.x=T)
  n1.results <- subset(results, order=="negfirst_1")
  n1.results <- merge(n1.results, n1.cond, all.x=T)
  n2.results <- subset(results, order=="negfirst_2")
  n2.results <- merge(n2.results, n2.cond, all.x=T)
  
  allresults <- rbind(p1.results, p2.results, n1.results, n2.results)
  allresults <- allresults[with(allresults, order(allresults$Subject, allresults$group)),]
  
  
  # type of trial
  fillerconds <- c("FMN", "FSN", "FMP", "FSP")
  posconds <- c("TFP", "TRP", "TWP", "TCP", "FSP", "FMP")
  negconds <- c("TFN", "TRN", "TWN", "TCN", "FSN", "FMN")
  allresults$label <- ifelse(allresults$condition=="practice", "practice", 
                             ifelse(allresults$condition %in% fillerconds, "filler", "target"))
  allresults$polarity <- ifelse(allresults$condition %in% posconds, "pos", "neg")
  
  allresults$story <- ifelse(allresults$condition %in% c("TRP", "TRN"), "reach",
                             ifelse(allresults$condition %in% c("TFP", "TFN"), "fit",
                                    ifelse(allresults$condition %in% c("TWP", "TWN"), "lift",
                                           ifelse(allresults$condition %in% c("TCP", "TCN"), "capacity", 
                                                  ifelse(allresults$condition %in% c("FSN", "FSP"), "sizematch", 
                                                         ifelse(allresults$condition %in% c("FMP", "FMN"), "colormatch",
                                                                ifelse(allresults$condition == "practice", "practice", "error")))))))
  
  
  rm(n1,n2,p1,p2,n1.cond,n1.results,n2.cond,n2.results,p1.cond,p1.results,p2.cond,p2.results, results,fillerconds,negconds,posconds, conditions.dataframe)
  
  just <- subset(allresults, grepl("justification", question))
  justifications <- data.frame(just$WorkerId, just$response, just$condition)
  colnames(justifications) = c("WorkerId", "justification", "condition")
  nonjustifications <- subset(allresults, ! grepl("justification", question))
  
  allresults <- merge(justifications, nonjustifications)
  
  # exploring for cheaters
  testingresults <- subset(allresults, label != "practice")
  
  testingresults$timeOut <- ifelse(!is.na(testingresults$responseTime) & testingresults$responseTime > 9999, 1, 0)
  testingresults$middle <- ifelse(testingresults$response==2, 1, 0)
  numtrials = length(unique(subset(allresults, Subject==1 & label!="practice")$group)) # 12
  subject.accuracy <- ddply(testingresults, .(WorkerId), summarise, accuracy=mean(correct, na.rm=T), timeOut=sum(timeOut), timeOutPercent=(sum(timeOut)/numtrials), order=unique(order))
  subject.accuracy = subject.accuracy[order(subject.accuracy$accuracy),]
  numfillers = length(unique(subset(allresults, label == "filler")$group)) # 4
  filler.subj.accuracy <- ddply(subset(testingresults, label=="filler"), .(WorkerId), summarise, filler.accuracy = mean(correct, na.rm=T), filler.timeOut=sum(timeOut), filler.timeOutPercent=(sum(timeOut)/numfillers), order=unique(order))
  filler.subj.accuracy <- filler.subj.accuracy[order(filler.subj.accuracy$filler.accuracy),]
  num2s <- ddply(subset(testingresults, label == "target"), .(WorkerId), summarise, num2s = sum(middle, na.rm=T))  
  subject.accuracy <- merge(subject.accuracy, filler.subj.accuracy)
  subject.accuracy <- merge(subject.accuracy, num2s)
  subject.accuracy = subject.accuracy[order(subject.accuracy$filler.accuracy),]
  
  subject.accuracy$exclude <- ifelse(subject.accuracy$filler.accuracy < 0.7 | subject.accuracy$timeOut > 3 | subject.accuracy$num2s >4 | subject.accuracy$WorkerId %in% manual_excludes, 1, 0)
  
  
  
  bad.subjects <- subset(subject.accuracy, exclude==1)$WorkerId 
  
  
  #write.csv(subject.accuracy, "subject_accuracy_allbatches.csv")
  
  allresults$exclude <- ifelse(allresults$WorkerId %in% bad.subjects, 1, 0) 
  good.results <- subset(allresults, exclude==0)
  
  #write.csv(allresults, "allresults_withexclude.csv", row.names=FALSE)
  #write.csv(good.results, "goodresults_allbatches.csv", row.names=FALSE)
  
  
  #counts <- ddply(good.results, .(order), summarise, freq = length(unique(WorkerId)))
  #counts
  #write.csv(counts, "participant_counts_02-24-20.csv", row.names=F)
  
  #unprocessed_data <- subset(unprocessed_data, label != "practice")
  
  #get just target data, filter out timeouts
  #filtered_data <- subset(unprocessed_data, polarity=="pos" | polarity=="neg")
  
  #filtered_data$age_group <- as.character(filtered_data$age_group)
  
  #add opposite/middle columns
  #filtered_data$opposite <- ifelse(filtered_data$response_type=="opposite", 1, 0)
  #filtered_data$middle <- ifelse(filtered_data$response_type=="middle", 1, 0)
  
  
  
  # accuracy check and exclusion of low-accuracy participants
  # Accuracy criterion for inclusion in most experiments is 75% total filler accuracy (as there is only one filler condition)
  # Accuracy criterion for inclusion in conjunction only is either 100% conjunction filler accuracy, or 50% conjunction filler accuracy and 75% total filler accuracy
  
  target.accuracy <- ddply(good.results, .(WorkerId, polarity), summarise, target.accuracy=mean(correct, na.rm=TRUE))
  #filler.accuracy <- ddply(subset(unprocessed_data, label=="filler"), .(WorkerId), summarise, filler.accuracy = mean(correct, na.rm=TRUE))
  
  #target.rt <- ddply(subset(filtered_data, responseTime < 9999), .(WorkerId, polarity), summarise, target.rt=mean(responseTime))
  
  
  #al.accuracy_new <- ddply(subset(filtered_data, label=="target"), .(age_group, polarity), summarise, al_sd=sd(correct, na.rm=TRUE), al_accuracy=mean(correct, na.rm=TRUE), numobvs=length(correct))
  #middle.accuracy_new <- ddply(subset(filtered_data, label=="target"), .(age_group, polarity), summarise, mid_sd=sd(middle, na.rm=TRUE), mid_accuracy=mean(middle, na.rm=TRUE))
  #opposite.accuracy_new <- ddply(subset(filtered_data, label=="target"), .(age_group, polarity), summarise, opp_sd=sd(opposite, na.rm=TRUE), opp_accuracy=mean(opposite, na.rm=TRUE))
  
  
  #al.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(correct, na.rm=TRUE), numobvs=length())
  #al.sd <- ddply(al.accuracy, .(age_group, polarity), summarise, al_se=sd(accuracy, na.rm=TRUE)/sqrt(al_sd=sd(accuracy, na.rm=TRUE), al_accuracy=mean(accuracy, na.rm=TRUE))
  
  
  #middle.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(middle, na.rm=TRUE))
  #middle.sd <- ddply(middle.accuracy, .(age_group, polarity), summarise, mid_sd=sd(accuracy, na.rm=TRUE), mid_accuracy=mean(accuracy, na.rm=TRUE))
  
  #opposite.accuracy <- ddply(subset(filtered_data, label=="target"), .(subject, age_group, polarity), summarise, accuracy=mean(opposite, na.rm=TRUE))
  #opposite.sd <- ddply(opposite.accuracy, .(age_group, polarity), summarise, opp_sd=sd(accuracy, na.rm=TRUE), opp_accuracy=mean(accuracy, na.rm=TRUE))
  
  
  #unprocessed_data <- merge(unprocessed_data, overall.accuracy)
  #unprocessed_data <- merge(unprocessed_data, filler.accuracy)
  unprocessed_data <- merge(good.results, target.accuracy)
  unprocessed_data <- merge(good.results, target.rt)
  
  # na.count <- ddply(filtered_data, .(WorkerId), summarise, na.count=sum(is.na(response)))
  # one.count <- ddply(filtered_data, .(WorkerId), summarise, one.count=sum(response=="1", na.rm=TRUE))
  # two.count <- ddply(filtered_data, .(WorkerId), summarise, two.count=sum(response=="2", na.rm=TRUE))
  # three.count <- ddply(filtered_data, .(WorkerId), summarise, three.count=sum(response=="3", na.rm=TRUE))
  # 
  # unprocessed_data <- merge(unprocessed_data, one.count)
  # unprocessed_data <- merge(unprocessed_data, two.count)
  # unprocessed_data <- merge(unprocessed_data, three.count)
  # unprocessed_data <- merge(unprocessed_data, na.count)
  
  # response type column
  unprocessed_data$responseType <- ifelse(unprocessed_data$response=="2", "mid", ifelse(unprocessed_data$correct==1, "adultlike", "opposite"))
  
  # other measures
  # log
  unprocessed_data$logRT = log(unprocessed_data$responseTime)
  
  # z score
  #p.means <- aggregate(unprocessed_data$responseTime, list(WorkerId = unprocessed_data$WorkerId), mean)
  #colnames(p.means)[2] = "mean"
  #p.sds <- aggregate(unprocessed_data$responseTime, list(WorkerId = unprocessed_data$WorkerId), sd)
  #colnames(p.sds)[2] = "sd"
  #p.data <- merge(p.means, p.sds, by="WorkerId")
  #unprocessed_data <- merge(unprocessed_data, p.data, by="WorkerId")
  #unprocessed_data$zScore = (unprocessed_data$responseTime - unprocessed_data$mean)/unprocessed_data$sd
  #unprocessed_data$mean <- NULL
  #unprocessed_data$sd <- NULL
  
  #percent.yes <- ddply(unprocessed_data, .(subject), summarise, percent.yes=mean(answer))
  
  #unprocessed_data <- merge(unprocessed_data, percent.yes)
  
  # Exclude bad participants
  # unprocessed_data$good.acc <- ifelse(unprocessed_data$filler.accuracy >= 0.65, 1, 0)
  # unprocessed_data$same.answer <- ifelse(unprocessed_data$one.count >= 7 |
  #                                          unprocessed_data$two.count >= 7 |
  #                                          unprocessed_data$three.count >= 7 |
  #                                          unprocessed_data$na.count >= 4, 1, 0)
  
  
  # exclude bad participants
  #processed_data <- subset(unprocessed_data, good.acc == 1 & same.answer == 0)
  
  # insert a column for accuracy for each participant for each condition's accuracy
  #condition.accuracy <- ddply(processed_data, .(subject, condition), summarise, condition.accuracy=mean(correct))
  #processed_data <- merge(processed_data, condition.accuracy)
  
  
  return(unprocessed_data)
}



clean.adult.data.exp2 <- clean_adult_data_exp2()

```

```{r}
no_NA_exp2 <- droplevels(subset(clean.adult.data.exp2, !is.na(clean.adult.data.exp2$responseType)))

no_NA_exp2$responseType <- as.factor(no_NA_exp2$responseType)

model_MC_adult_exp2 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = logRT ~ (polarity + responseType)^2,
                     random = ~ WorkerId + condition,
                     family = "gaussian",
                     data = no_NA_exp2,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
```

```{r}
model_MC_adult_exp2_diag <- lapply(model_MC_adult_exp2, function(m) m$Sol)
model_MC_adult_exp2_diag <- do.call(mcmc.list, model_MC_adult_exp2_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_adult_exp2_diag, auto.layout=F)
gelman.diag(model_MC_adult_exp2_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_adult_exp2_diag, ask=F, auto.layout=F)
```

```{r}
model_MC_adult_exp2_combined <- bind_mcmc(model_MC_adult_exp2_diag)

adult_exp2_intercept <- model_MC_adult_exp2_combined[, 1]
adult_exp2_pos <- model_MC_adult_exp2_combined[, 2]
adult_exp2_mid <- model_MC_adult_exp2_combined[, 3]
adult_exp2_opp <- model_MC_adult_exp2_combined[, 4]
adult_exp2_posmid <- model_MC_adult_exp2_combined[, 5]
adult_exp2_posopp <- model_MC_adult_exp2_combined[, 6]

estimate_exp2 = function(polarity="neg", response_type="adult"){
  return(adult_exp2_intercept + 
         (polarity == "pos")*adult_exp2_pos +
         (response_type == "mid")*adult_exp2_mid +
         (response_type == "opp")*adult_exp2_opp +
         (polarity == "pos")*(response_type == "mid")*adult_exp2_posmid +
         (polarity == "pos")*(response_type == "opp")*adult_exp2_posopp)
}                    
```

Modeling response_type

```{r}
IJ <- (1/3) * (diag(2) + matrix(1,2, 2))
prior.MC_adult <- list(R = list(V = IJ, fix = 1),
                 G=list(G1=list(V        = diag(2),
                                n        = 2),
                        G2=list(V        = diag(2),
                                n        = 2)))


model_MC_adult_response_exp2 <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = responseType ~ -1 + trait + trait:polarity,
                     random = ~ us(trait):WorkerId + us(trait):condition,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     prior=prior.MC_adult,
                     data = no_NA_exp2,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)
```

Running diagnostics on chains

```{r}
model_MC_adult_response_exp2_diag <- lapply(model_MC_adult_response_exp1, function(m) m$Sol)
model_MC_adult_response_exp2_diag <- do.call(mcmc.list, model_MC_adult_response_exp2_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_adult_response_exp2_diag, auto.layout=F)
gelman.diag(model_MC_adult_response_exp2_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_adult_response_exp2_diag, ask=F, auto.layout=F)
```

```{r}
model_MC_adult_response_exp2_combined <- bind_mcmc(model_MC_adult_response_exp2_diag)

adult_exp2_response_int <- rescale(model_MC_adult_response_exp2_combined, 1:2)

adult_exp2_response_pos <- rescale(model_MC_adult_response_exp2_combined, 3:4)
```

Graphs

```{r}
library(tikzDevice)


generateTikzGraph <- function(file, width, height, gg) {
  tikz(file, width=width, height=height, sanitize=TRUE)
  print(gg)
  dev.off()
}

targ.al.plot.single <- function(indata, title="Adult-like by age group") { 
  ggplot(indata, aes(x=age_group, y=correct, fill=polarity, color=polarity, width=0.6)) +
    #stat_summary(fun.y="mean", geom="bar", position=p) +
    #stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.6, width=0.15, position=p) +
    theme(panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank()) +
    theme(axis.line=element_line(color="black"), axis.text=element_text(color="black"), axis.ticks=element_line(color="black")) +
    coord_cartesian(ylim=c(0, 1.0)) +
    scale_x_discrete("Age Group") +
    scale_y_continuous("% Correct") +
    ggtitle(title) +
    theme(plot.title = element_text(hjust = 0.5),
          panel.background = element_rect(fill = NA)) +
    geom_point(aes(shape=polarity), size=5, stat="summary", fun.y="mean") +
    geom_line(aes(group=polarity), stat="summary", fun.y="mean") # +
   # geom_errorbar(aes(ymin=HPDmin, ymax=HPDmax), width=.1)
}

no_NA_exp1$story <- revalue(no_NA_exp1$request, c("TCN_justification" = "fill", "TCP_justification" = "fill", "TFN_justification" = "fit", "TFP_justification" = "fit", "TRN_justification" = "reach", "TRP_justification" = "reach", "TWN_justification" = "weight", "TWP_justification" = "weight"))

no_NA_exp1$polarity <- no_NA_exp1$label

targ.al.plot.by_story.adult <- function(indata, title="Adult-like by story type") { 
  ggplot(indata, aes(x=story, y=correct, fill=polarity, color=polarity, width=0.6)) +
    #stat_summary(fun.y="mean", geom="bar", position=p) +
    #stat_summary(fun.data="mean_cl_boot", geom="errorbar", size=0.6, width=0.15, position=p) +
    theme(panel.background=element_blank(), panel.grid.major=element_blank(), panel.grid.minor=element_blank()) +
    theme(axis.line=element_line(color="black"), axis.text=element_text(color="black"), axis.ticks=element_line(color="black")) +
    coord_cartesian(ylim=c(0, 1.0)) +
    scale_x_discrete("Story type") +
    scale_y_continuous("% Correct") +
    ggtitle(title) +
    theme(plot.title = element_text(hjust = 0.5),
          panel.background = element_rect(fill = NA)) +
    geom_bar(size=5, position="dodge", stat="summary", fun.y="mean")
   # geom_errorbar(aes(ymin=HPDmin, ymax=HPDmax), width=.1)
}


```

Running RealOpp analysis

```{r}

exp1_adult_real_opp <- read.csv("../data/exp1-adult/real_opp.csv", header=TRUE, na.strings="NULL", stringsAsFactors = FALSE)

no_NA_exp1_realopp <- no_NA_exp1

no_NA_exp1_realopp$WorkerId <- as.character(no_NA_exp1_realopp$WorkerId)

no_NA_exp1_realopp <- merge(no_NA_exp1_realopp, exp1_adult_real_opp, by=c("WorkerId", "item"))

no_NA_exp1_realopp$WorkerId <- as.factor(no_NA_exp1_realopp$WorkerId)

levels(no_NA_exp1_realopp$responseType) <- c(levels(no_NA_exp1_realopp$responseType), "realopp")

no_NA_exp1_realopp$responseType[no_NA_exp1_realopp$realopp == 1] <- "realopp"

model_MC_adult_exp1_realopp <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = logRT ~ (label + responseType)^2,
                     random = ~ WorkerId + request,
                     family = "gaussian",
                     data = targ(no_NA_exp1_realopp),
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)

IJ_realopp <- (1/3) * (diag(3) + matrix(1,3, 3))
prior.MC_adult_realopp <- list(R = list(V = IJ_realopp, fix = 1),
                 G=list(G1=list(V        = diag(3),
                                n        = 3),
                 G2=list(V               = diag(3),
                                n        = 3)))


model_MC_adult_response_exp1_realopp <- mclapply(1:4, function(i) {
MCMCglmm(fixed = responseType ~ -1 + trait + trait:label,
                     random = ~ us(trait):WorkerId + us(trait):request,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     prior=prior.MC_adult_realopp,
                     data = no_NA_exp1_realopp,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)


```


```{r}
model_MC_adult_exp1_realopp_diag <- lapply(model_MC_adult_exp1_realopp, function(m) m$Sol)
model_MC_adult_exp1_realopp_diag <- do.call(mcmc.list, model_MC_adult_exp1_realopp_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_adult_exp1_realopp_diag, auto.layout=F)
gelman.diag(model_MC_adult_exp1_realopp_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_adult_exp1_realopp_diag, ask=F, auto.layout=F)
```

```{r}
model_MC_adult_exp1_realopp_combined <- bind_mcmc(model_MC_adult_exp1_realopp_diag)

adult_exp1_realopp_intercept <- model_MC_adult_exp1_realopp_combined[, 1]
adult_exp1_realopp_pos <- model_MC_adult_exp1_realopp_combined[, 2]
adult_exp1_realopp_mid <- model_MC_adult_exp1_realopp_combined[, 3]
adult_exp1_realopp_opp <- model_MC_adult_exp1_realopp_combined[, 4]
adult_exp1_realopp_realopp <- model_MC_adult_exp1_realopp_combined[, 5]
adult_exp1_realopp_posmid <- model_MC_adult_exp1_realopp_combined[, 6]
adult_exp1_realopp_posopp <- model_MC_adult_exp1_realopp_combined[, 7]
adult_exp1_realopp_posrealopp <- model_MC_adult_exp1_realopp_combined[, 8]


estimate_exp1_realopp = function(polarity="neg", response_type="adult"){
  return(exp(adult_exp1_realopp_intercept + 
         (polarity == "pos")*adult_exp1_realopp_pos +
         (response_type == "mid")*adult_exp1_realopp_mid +
         (response_type == "opp")*adult_exp1_realopp_opp +
         (response_type == "realopp")*adult_exp1_realopp_realopp +
         (polarity == "pos")*(response_type == "mid")*adult_exp1_realopp_posmid +
         (polarity == "pos")*(response_type == "opp")*adult_exp1_realopp_posopp +
         (polarity == "pos")*(response_type == "realopp")*adult_exp1_realopp_posrealopp))

}                    
```

```{r}
model_MC_adult_exp1_realopp_response_diag <- lapply(model_MC_adult_response_exp1_realopp, function(m) m$Sol)
model_MC_adult_exp1_realopp_response_diag <- do.call(mcmc.list, model_MC_adult_exp1_realopp_response_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_adult_exp1_realopp_response_diag, auto.layout=F)
gelman.diag(model_MC_adult_exp1_realopp_response_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_adult_exp1_realopp_response_diag, ask=F, auto.layout=F)
```

```{r}

exp2_adult_real_opp <- read.csv("../data/exp2-adult/real_opp.csv", header=TRUE, na.strings="NULL", stringsAsFactors = FALSE)

no_NA_exp2_realopp <- no_NA_exp2

no_NA_exp2_realopp$WorkerId <- as.character(no_NA_exp2_realopp$WorkerId)

no_NA_exp2_realopp <- merge(no_NA_exp2_realopp, exp2_adult_real_opp, by=c("WorkerId", "condition"))

no_NA_exp2_realopp$WorkerId <- as.factor(no_NA_exp2_realopp$WorkerId)

levels(no_NA_exp2_realopp$responseType) <- c(levels(no_NA_exp2_realopp$responseType), "realopp")

no_NA_exp2_realopp$responseType[no_NA_exp2_realopp$realopp == 1] <- "realopp"


no_NA_exp2_realopp <- subset(no_NA_exp2_realopp, label=="target")

model_MC_adult_exp2_realopp <- mclapply(1:4, function(i) {
  MCMCglmm(fixed = logRT ~ (polarity + responseType)^2,
                     random = ~ WorkerId + condition,
                     family = "gaussian",
                     data = no_NA_exp2_realopp,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)

IJ_realopp <- (1/3) * (diag(2) + matrix(1,2,2))
prior.MC_adult_realopp <- list(R = list(V = IJ_realopp, fix = 1),
                 G=list(G1=list(V        = diag(2),
                                n        = 2),
                 G2=list(V               = diag(2),
                                n        = 2)))


no_NA_exp2_realopp$responseType[no_NA_exp2_realopp$responseType == "opposite"] <- "mid"

no_NA_exp2_realopp <- droplevels(no_NA_exp2_realopp)

model_MC_adult_response_exp2_realopp <- mclapply(1:4, function(i) {
MCMCglmm(fixed = responseType ~ -1 + trait + trait:polarity,
                     random = ~ us(trait):WorkerId + us(trait):condition,
                     rcov = ~ us(trait):units,
                     family = "categorical",
                     prior=prior.MC_adult_realopp,
                     data = no_NA_exp2_realopp,
                     thin = 50,
                     burnin = 10000,
                     nitt = 400000,
                     verbose = FALSE)
}, mc.cores=4)


```

```{r}
model_MC_adult_exp2_realopp_response_diag <- lapply(model_MC_adult_response_exp2_realopp, function(m) m$Sol)
model_MC_adult_exp2_realopp_response_diag <- do.call(mcmc.list, model_MC_adult_exp2_realopp_response_diag)

par(mfrow=c(4,2), mar=c(2,2,1,2))
gelman.plot(model_MC_adult_exp2_realopp_response_diag, auto.layout=F)
gelman.diag(model_MC_adult_exp2_realopp_response_diag)

par(mfrow=c(2,2), mar=c(2, 1, 1, 1))
plot(model_MC_adult_exp2_realopp_response_diag, ask=F, auto.layout=F)
```
